Study of Intra- and Inter-Job Interference with Different Job allocations

### 2015-10-15 submission.tex
update the cited webpage in bib file

We selected three signature applications from DOE Design Forward Project\cite{design forward webpage} as examples to conduct detailed study about their communication patterns. We use a sophisticated simulation toolkit named CODES, Co-Design of Multi-layer Exascale Storage Architecture\cite{Jason-2011}, from Argonne National Laboratory as a research vehicle to evaluate the performance of these applications with various allocations. We analyze the intra- and inter-job interference by simulating applications running exclusively or concurrently with different allocations.

@@

There are many applications running on HPC systems like Mira \cite{bgq} and Titan \cite{titan}. Most of these applications are parallel and communication intensive, and conform to different communication patterns. In this work, we select three representative applications from DOE Design Forward project \cite{design forward webpage}. Each application conforms to a distinctive communication pattern that is commonly seen from applications in HPC workload. We believe these three applications can represent a big group of applications that conform to similar communication patterns. The applications studied in this work are Algebraic MultiGrid Solver(AMG), Geometric MultiGrid(MultiGrid) and CrystalRouter. The communication pattern figures we present in Section \ref{sec:amg}, \ref{sec:crystalrouter}, \ref{sec:multigrid} are generated with the IPM \cite{ipm} data from \cite{design forward webpage}.

% MiniApps are reduced proxy applications that encapsulate the salient performance of larger full size applications \cite{miniapp}. Since we only focus on the dominant communication pattern of parallel applications, these MiniApps are perfect candidates for analysis the application's performance on different allocations or on new network architectures. We choose three MiniApps, namely, Algebraic Multigrid Solver(AMG), Geometric MultiGrid(MultiGrid) and CrystalRouter. Their representative communication patterns that are commonly seen in the HPC system workload. The communication pattern figures we present here are generated with the IPM \cite{ipm} data from \cite{design forward webpage}.

@@

AMG represents a group of applications whose dominant communication pattern is Nearest Neighbor. Applications with such similar dominant communication pattern are like PARTISN, SNAP \cite{design forward webpage}.

@@

MultiGrid represents a group of applications whose dominant communication pattern is Many-to-Many (some literatures also refer it as All-to-All \cite{roth}).  Applications with such similar dominant communication pattern are like FillBoundary and MiniDFT \cite{design forward webpage}.

@@

%We summarize the benchmarks and MiniApps on DOE design forward webpage\cite{design forward webpage}, as shown in Table \ref{tab: app summary}. According to their dominant communication patterns, there are three categories, namely Nearest Neighbor, All-to-All and 3D Lattice. The three applications studies in this work are representative for different categories.

@@

%\textbf{P2: communication characteristics}\\
Some research institutes put great effort in characterization of scientific applications. The Department of Energy initiate this design forward project aims at the identification of the computational characteristics of the DOE MiniApps developed at various exascale co-design centers \cite{design forward webpage}. In this project, the communication patterns of several DOE full applications and associated mini-applications are studied to provide a more complete snapshot of the DOE workload. A joint project named CORAL from Oak Ridge, Argonne and Livermore provide a series of benchmarks to represent DOE workloads and technical requirements \cite{coral}. The CORAL project includes scalable science benchmarks, throughput benchmarks, data centric benchmarks, skeleton benchmarks and Micro benchmarks.

>>>>

We selected three signature applications from DOE Design Forward Project\cite{designforwardwebpage} as examples to conduct detailed study about their communication patterns. We use a sophisticated simulation toolkit named CODES, Co-Design of Multi-layer Exascale Storage Architecture\cite{Jason-2011}, from Argonne National Laboratory as a research vehicle to evaluate the performance of these applications with various allocations. We analyze the intra- and inter-job interference by simulating applications running exclusively or concurrently with different allocations.

@@

There are many applications running on HPC systems like Mira \cite{bgq} and Titan \cite{titan}. Most of these applications are parallel and communication intensive, and conform to different communication patterns. In this work, we select three representative applications from DOE Design Forward project \cite{designforwardwebpage}. Each application conforms to a distinctive communication pattern that is commonly seen from applications in HPC workload. We believe these three applications can represent a big group of applications that conform to similar communication patterns. The applications studied in this work are Algebraic MultiGrid Solver(AMG), Geometric MultiGrid(MultiGrid) and CrystalRouter. The communication pattern figures we present in Section \ref{sec:amg}, \ref{sec:crystalrouter}, \ref{sec:multigrid} are generated with the IPM \cite{ipm} data from \cite{designforwardwebpage}.

% MiniApps are reduced proxy applications that encapsulate the salient performance of larger full size applications \cite{miniapp}. Since we only focus on the dominant communication pattern of parallel applications, these MiniApps are perfect candidates for analysis the application's performance on different allocations or on new network architectures. We choose three MiniApps, namely, Algebraic Multigrid Solver(AMG), Geometric MultiGrid(MultiGrid) and CrystalRouter. Their representative communication patterns that are commonly seen in the HPC system workload. The communication pattern figures we present here are generated with the IPM \cite{ipm} data from \cite{designforwardwebpage}.

@@

AMG represents a group of applications whose dominant communication pattern is Nearest Neighbor. Applications with such similar dominant communication pattern are like PARTISN, SNAP \cite{designforwardwebpage}.

@@

MultiGrid represents a group of applications whose dominant communication pattern is Many-to-Many (some literatures also refer it as All-to-All \cite{roth}).  Applications with such similar dominant communication pattern are like FillBoundary and MiniDFT \cite{designforwardwebpage}.

@@

%We summarize the benchmarks and MiniApps on DOE design forward webpage\cite{designforwardwebpage}, as shown in Table \ref{tab: app summary}. According to their dominant communication patterns, there are three categories, namely Nearest Neighbor, All-to-All and 3D Lattice. The three applications studies in this work are representative for different categories.

@@

%\textbf{P2: communication characteristics}\\
Some research institutes put great effort in characterization of scientific applications. The Department of Energy initiate this design forward project aims at the identification of the computational characteristics of the DOE MiniApps developed at various exascale co-design centers \cite{designforwardwebpage}. In this project, the communication patterns of several DOE full applications and associated mini-applications are studied to provide a more complete snapshot of the DOE workload. A joint project named CORAL from Oak Ridge, Argonne and Livermore provide a series of benchmarks to represent DOE workloads and technical requirements \cite{coral}. The CORAL project includes scalable science benchmarks, throughput benchmarks, data centric benchmarks, skeleton benchmarks and Micro benchmarks.
